---
output: html_document
---

While you have already quite a lot experience in handling data from your 
course on data management, it does not hurt to get some more hints for filename
manipulations or collecting information in text files.

### Hints on manipulating filenames

Splitting informatino on the path and filename can be done quite handy using the
`basename()` and `dirname()` functions of R's base package.

In addition, the following code line might be help if you want to split and 
recombine filenames based on a certain character or character sequenze in these
filenames. For example, the following code returns the position of the split
pattern "_B" in the filename part of the variable `filepath` which holds full 
path and name of a data file:
```{r, eval=FALSE}
split_pattern <- "_B"
 pos <- gregexpr(pattern =split_pattern, sub("(.+)[.][^.]+$", "\\1", 
                                             basename(filepath)))[[1]][1]
```


### Hints on collecting metainformation
If you want to collect specific metainformation from a text file, several things
have to be considered.

First, you must somehow read the file. If the file contains some kind of
deliminater between the key words and the actual values, use it and remember
that a deliminator can also be something like "<" or "=" etc.

Second, you must somehow tell the program what keywords you are looking for.
Hence, it it might be a good idea to start with defining the respective search 
terms, i.e. the character strings you are looking for. Here's an example from
a script which analysis Landsat 8 metadata:
```{r, eval=FALSE}
search_term_add_ref <- paste0("REFLECTANCE_ADD_BAND_", bandnumber)
```

Third, you have to get the respective data line which contains your keyword
and extract the information. Given the search variable from above and given that
your metadata is somehow stored in a dataframe called `metadata` which contains
the keyword you are looking for in the first column (V1) and the value you are 
looking vor in the second column (V2), such a code line could look like this:
```{r, eval=FALSE}
cal_add_ref <- as.numeric(as.character(
  (subset(metadata$V2, gsub("\\s","", metadata$V1) == search_term_add_ref))))
```

Fourth, you have to store the results in some kind of list or data frame.

Fifth, if your metadata has e.g. band specific information, you might have to
collect the information for each band, hense, you have to repeat steps two to
four several times and combine everything in the end. It does not matter if you
use a for-loop or an lapply-loop, but the latter comes with a little less 
overhead since you do not have to define empty storage variables to hold the
results of each iteration first. So, an lapply-loop structure for such a problem
can look like that:
```{r, eval=FALSE}
metainformation <- lapply(seq(1:number_of_bands), function(x){
  # This loop iterates x from 1 to the value of the variable number_of_bands
  # Define search terms
  ...
  
  # Get metainformation based on search terms
  ...
  
  # Handle special cases (e.g. if certain metainformation is only available for
  # a subset of the lapply loops)
  ...
  
  # Store actual results in a data frame
  ...
  })
  # Combine individual results from the lapply loops into a single data frame
  metainformation_all <- do.call("rbind", metainformation)
```

Please note that the above example assumes that you store your loop results
in a data frame. Of course this can be soleved with other objects, too, but then
the last line of the code will not work.
