---
title: "W11-1: Variable selection and model tuning"
output: html_document
---

In order to speed things up a little, here is a template for a markdown file
which can be used as part of this worksheet.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(rgdal)
library(sp)
library(caret)

inpath_ecol <- "D:/active/moc/am-remote-sensing/examples/data/ecology/2015/"
```


### Function for scaling datasets
```{r}
scale <- function(df){
  df_means <- colMeans(df, na.rm = TRUE)
  df_sds <- apply(df, 2, sd, na.rm=TRUE)
  df_scale <- lapply(seq(ncol(df)), function(x){
    (df[,x] - df_means[x]) / df_sds[x]
    })
  df_scale <- do.call ("cbind", df_scale)
  colnames(df_scale) <- colnames(df)
  return(df_scale)
  }
```


### Function for creating training and testing datasets
```{r}
traintest_df <- function(pred, resp, times = 1, p = 0.75, list = FALSE){
  train_ids <- createDataPartition(resp, times = times, p = p, list = list)

  train_resp <- resp[train_ids]
  train_pred <- pred[train_ids, ]
  
  test_resp <- resp[-train_ids]
  test_pred <- pred[-train_ids, ]
  return(list(train_resp, train_pred, test_resp, test_pred))
  }
```


### Read datasets
Read datasets
```{r}
ecol_db <- readOGR(paste0(inpath_ecol, "ecol_db.shp"), layer = "ecol_db")
ecol_db <- data.frame(ecol_db)
ecol_hg <- readOGR(paste0(inpath_ecol, "ecol_hg.shp"), layer = "ecol_hg")
ecol_hg <- data.frame(ecol_hg)
```


### Select response variable and scale predictors
Make sure that the response is a factor (if you want classification)
```{r}
ecol <- ecol_hg

coln_resp <- which(names(ecol) == "d12_k5")
coln_pred <- c(which(names(ecol)=="re01"):which(names(ecol)=="zrsd"))

resp <- ecol[, coln_resp]
pred <- ecol[, coln_pred]

pred_scale <- scale(pred)
summary(pred_scale)

# pred_scale <- rbind(pred_scale, pred_scale*1.20, pred_scale*0.80)
# resp <- factor(c(as.character(resp), as.character(resp), as.character(resp)))
```


### Create training and independent validation data sample
Consider that the respone variable should be sampled in a stratified manner.
```{r}
l <- traintest_df(pred = pred_scale, resp = resp, p = 0.80)
train_resp <- l[[1]]
train_pred <- l[[2]]
test_resp <- l[[3]]
test_pred <- l[[4]]
```

### Set recursive feature selection parameters
```{r}

```

### Set model tuning parameters
```{r}

```

### Train model incl. recursive feature elimination
```{r}

# Save model
save(<my-model>, file = "myFile.RData")
```

