---
title: "W05-3: Accuracy"
output: html_document
---

In order to speed things up a little, here is a template for a markdown file
which can be used as part of this worksheet.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(raster)
library(rgdal)
library(sp)

inpath_lc <- "D:/active/moc/am-remote-sensing/examples/data/landcover/"
inpath_ts <- "D:/active/moc/am-remote-sensing/examples/data/landcover/"
```

### Function for computing kappa
Function to compute kappa based on ...
```{r}
compKappa <- function(# Your code here){
  # Your code here
  }
```

### Reading land-cover classification and training site data
Read classification and training site information (assuming that you have 
followed W04-x and W05-x to the minute).
```{r}
lc <- raster(paste0(inpath_lc,"l8_lc_rf.tif"))
ts <- readOGR(paste0(inpath_ts, "l8_lc_training_areas_all.shp"), 
              layer = "l8_lc_training_areas_all")
```

### Extract validation data pairs and compute contingency table
```{r}
# Your code here
# The ftable function might be useful.
```

### Compute kappa
```{r}
# Your code here
```
