---
title: "W02-2: Dark object substraction"
output: html_document
---

In order to speed things up a little, here is a template for a markdown file
which can be used as part of this worksheet.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(raster)
library(rgdal)
library(sp)

library(devtools)
install_git("git://github.com/environmentalinformatics-marburg/satellite")
library(satellite)

inpath_l8 <- "D:/active/moc/am-remote-sensing/examples/data/landsat/l8_2013-07-07/"
```

### Reading croped landsat 8 data
Read multi-layer geotiff in a stack and adjust the layer names to match the 
actual band numbers (assuming that you have followed W02-2 to the minute).
Read multi-layer geotiff in a stack and adjust the layer names to match the 
actual band numbers (assuming that you have followed W01-1 to the minute).
```{r}
landsat_8 <- stack(paste0(inpath_l8,"l8_2013-07-07_30m_crop.tif"))
bands <- names(landsat_8)
pos <- gregexpr(pattern ='crop', bands)[[1]][1]
bands <- paste0(substr(bands, 1, pos + 3), "_", c(1:7, 9:11))
names(landsat_8) <- bands
names(landsat_8)
```

### Get metadata information
Get calibration coefficients from the metadata file using function 
"satellite::compMetalandsat_8". Adjust resulting data frame so it contains only
the bands which are part of the landsat_8 stack.
```{r}
meta <- compMetaLandsat(paste0(inpath_l8, "LC81950252013188LGN00_MTL.txt"))
meta <- meta[!is.na(meta$SPECTRUM) & meta$SRES == 30, ]

```

### Compute the top-of atmosphere solar irradiance
First, compute top of atmosphere solar irradiance:
```{r}
e_sun <- calcTOAIrradRadRef(rad_max = meta$RADMAX, 
                            ref_max = meta$REFMAX, 
                            normalize = FALSE,
                            esd = meta$ESD)
```

### Compute path radiance
Second, get the DN of a dark object in band x and compute the path radiance for
all bands.
```{r}
dodn <- calcDODN(landsat_8[[2]])

path_radiance <- calcPathRadDOS(dodn, bnbr = 2, 
                                band_wls = data.frame(meta$LMIN, meta$LMAX), 
                                radm = meta$RADM, 
                                rada = meta$RADA, 
                                szen = meta$SZEN, 
                                esun = e_sun, 
                                model = "DOS2", scat_coef = -4, 
                                dos_adjust = 0.01)
```


### Compute the atmospheric correction
Convert band DNs to radiance and compute atmospheric correction.
```{r}
landsat_8_rad <- calibLinear(band = landsat_8, 
                     mult = meta$RADM, 
                     add = meta$RADA)

landsat_8_ac <- calcAtmosCorr(sensor_rad = landsat_8_rad,
                              path_rad = path_radiance, 
                              esun = e_sun,
                              szen = meta$SZEN, 
                              model = "DOS2")
```

### Convert reflectance back to radiance
```{r}
landsat_8_ac_rad <- calibLinearInverse(landsat_8_ac,
                                       ref_mult = meta$REFM, 
                                       ref_add = meta$REFA,
                                       rad_mult = meta$RADM,
                                       rad_add = meta$RADA,
                                       szen = meta$SZEN)

```


### Save the corrected Landsat 8 data
Save bands 1 to 9 only.
```{r}
writeRaster(landsat_8_ac_rad[[1:8]], 
            filename = paste0(inpath_l8, "l8_2013-07-07_30m_crop_ac_rad.tif"),
                              format = "GTiff", overwrite = TRUE)
  ```
