---
title: "W02-1: From DNs to physical units"
output: html_document
---

In order to speed things up a little, here is a template for a markdown file
which can be used as part of this worksheet.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(raster)
library(rgdal)
library(sp)

library(devtools)
install_git("git://github.com/environmentalinformatics-marburg/satellite")
library(satellite)

inpath_l8 <- "D:/active/moc/am-remote-sensing/examples/data/landsat/l8_2013-07-07/"
```

### Reading croped Landsat 8 data
Read multi-layer geotiff in a stack and adjust the layer names to match the 
actual band numbers (assuming that you have followed W01-1 to the minute).
```{r}
landsat_8 <- stack(paste0(inpath_l8,"l8_2013-07-07_30m_crop.tif"))
bands <- names(landsat_8)
pos <- gregexpr(pattern ='crop', bands)[[1]][1]
bands <- paste0(substr(bands, 1, pos + 3), "_", c(1:7, 9:11))
names(landsat_8) <- bands
names(landsat_8)
```

### Get metadata information
Get calibration coefficients from the metadata file using function 
"satellite::compMetaLandsat"
```{r}
meta <- compMetaLandsat(paste0(inpath, "LC81950252013188LGN00_MTL.txt"))
```

### Define the function for unit conversion
```{r}
calibLinear <-  function(x, mult, add, szen, k1, k2){
  result <- mult * x + add
  if(!missing(szen)){
    result <- result / cos(szen * pi / 180.0)
  }
  if(!missing(k1)){
    result <- k2 / log(k1 / result + 1)
  }
  return(result)
}
```


### Converting band 3 and 10 to radiance
As an example, band 3 and 10 will be converted to radiance:
```{r}
band_03_rad <- calibLinear(landsat_8[[grep("crop_3", names(landsat_8))]], 
                           mult = meta$RADM[meta$BCDE == "B003n"],
                           add = meta$RADA[meta$BCDE == "B003n"])

band_10_rad <- calibLinear(landsat_8[[grep("crop_10", names(landsat_8))]], 
                           mult = meta$RADM[meta$BCDE == "B010n"],
                           add = meta$RADA[meta$BCDE == "B010n"])
writeRaster(band_03_rad, 
            filename = paste0(inpath, "l8_2013-07-07_band_03_rad.tif"),
                              format = "GTiff", overwrite = TRUE)
writeRaster(band_10_rad, 
            filename = paste0(inpath, "l8_2013-07-07_band_10_rad.tif"),
                              format = "GTiff", overwrite = TRUE)
# plot(band_03_rad)
# plot(band_10_rad)
```

### Converting band 3 to reflectance
As an example, band 3 will be converted to reflectance:
```{r}
band_03_ref <- calibLinear(landsat_8[[grep("crop_3", names(landsat_8))]], 
                           mult = meta$REFM[meta$BCDE == "B003n"],
                           add = meta$REFA[meta$BCDE == "B003n"])
writeRaster(band_03_ref, 
            filename = paste0(inpath, "l8_2013-07-07_band_03_ref.tif"),
                              format = "GTiff", overwrite = TRUE)
# plot(band_03_ref)
```

### Converting band 10 to brightness temperature
As an example, band 10 will be converted to brightness temperature:
```{r}
band_10_bt <- calibLinear(landsat_8[[grep("crop_10", names(landsat_8))]], 
                          mult = meta$RADM[meta$BCDE == "B010n"],
                          add = meta$RADA[meta$BCDE == "B010n"],
                          k1 = meta$BTK1[meta$BCDE == "B010n"],
                          k2 = meta$BTK2[meta$BCDE == "B010n"])
writeRaster(band_10_bt, 
            filename = paste0(inpath, "l8_2013-07-07_band_10_bt.tif"),
                              format = "GTiff", overwrite = TRUE)
# plot(band_10_bt)
```
