---
title: "W09-2: Bundling the perfect sensors"
output: html_document
---

In order to speed things up a little, here is a template for a markdown file
which can be used as part of this worksheet.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(raster)
library(rgdal)
library(sp)

# Your code here
```

### Load remote sensing data and provide meaningful layer names
```{r}
# Your code here
```

### Project satellite sensor data on lidar geometry and save stacks
If you followed the plan, all your data has a matching geometry so the only thing
left is to resample your satellite datasets to the extend of the two
LiDAR datsets which already match the area of the investigation sites.
```{r}
# Your code here
```

### Save names of stack layer as Rdata
```{r}
# Something like this:
names_hg <- c("re01", "re02", "re03", "re04", "re05", 
              "repca01", "repca2", "repca03", "repca04", "repca05", 
              "remean", "revar", "reskew", "rekurt", 
              "l801", "l802", "l803", "l804", "l805", "l806", "l807", "l809", 
              "l8pca01", "l8pca02", "l8pca03", "l8pca04", "l8pca5", "l8pca6", 
              "l8pca07", "l8pca09", 
              "l8mean", "l8var", "l8skew", "l8kurt", 
              "c02", "c02mean", "c02max", "c02sd",
              "c13", "c13mean", "c13max", "c13sd",
              "intm", "intmmean", "intmmax", "intmsd",
              "intr", "intrmean", "intrmax", "intrsd",
              "retm", "retmmean", "retmmax", "retmsd",
              "zr", "zrmean", "zrmax", "zrsd")

names_db <- c("re01", "re02", "re03", "re04", "re05", 
              "repca01", "repca2", "repca03", "repca04", "repca05", 
              "remean", "revar", "reskew", "rekurt", 
              "l801", "l802", "l803", "l804", "l805", "l806", "l807", "l809", 
              "l8pca01", "l8pca02", "l8pca03", "l8pca04", "l8pca5", "l8pca6", 
              "l8pca07", "l8pca09", 
              "l8mean", "l8var", "l8skew", "l8kurt", 
              "c02", "c02mean", "c02max", "c02sd",
              "c13", "c13mean", "c13max", "c13sd",
              "intm", "intmmean", "intmmax", "intmsd",
              "intr", "intrmean", "intrmax", "intrsd",
              "retm", "retmmean", "retmmax", "retmsd",
              "zr", "zrmean", "zrmax", "zrsd")

save(names_hg, names_db, file = paste0(inpath_ecol, "rs_stack_names.Rdata"))
```
