---
title: "W02-2: Dark object substraction"
output: html_document
---

In order to speed things up a little, here is a template for a markdown file
which can be used as part of this worksheet.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(raster)
library(rgdal)
library(sp)

library(devtools)
install_git("git://github.com/environmentalinformatics-marburg/satellite")
library(satellite)

inpath_l8 <- "D:/active/moc/am-remote-sensing/examples/data/landsat/l8_2013-07-07/"
```

### Reading croped Landsat 8 data
Read multi-layer geotiff in a stack and adjust the layer names to match the 
actual band numbers (assuming that you have followed W01-1 to the minute).
```{r}
landsat_8 <- stack(paste0(inpath_l8,"l8_2013-07-07_30m_crop.tif"))
bands <- names(landsat_8)
pos <- gregexpr(pattern ='crop', bands)[[1]][1]
bands <- paste0(substr(bands, 1, pos + 3), "_", c(1:7, 9:11))
names(landsat_8) <- bands
names(landsat_8)
```

### Get metadata information
Get calibration coefficients from the metadata file using function 
`satellite::compMetalandsat_8`. Adjust resulting data frame so it contains only
the bands which are part of the Landsat 8 stack.
```{r}
meta <- compMetaLandsat(paste0(inpath, "LC81950252013188LGN00_MTL.txt"))
meta <- meta[!is.na(meta$SPECTRUM) & meta$SRES == 30, ]

```

### Compute atmospheric correction
Read the help of the `satellite::calcAtmosCorr` function and come up with a step
by step guide on what to compute first:
 * Compute ...
 * Compute ...
 * Compute ...
 * Compute ...
 * Compute ...
```{r}
# Your code here
```

### Convert reflectance back to radiance
This last topic is not necesseraly required but since we want to combine the
Landsat 8 data with Landsat 7 and RapidEye later and since we want to use
radiances, let's convert the atmospheric corrected reflectance back to
radiance.
```{r}
landsat_8_ac_rad <- calibLinearInverse(landsat_8_ac,
                                       ref_mult = meta$REFM, 
                                       ref_add = meta$REFA,
                                       rad_mult = meta$RADM,
                                       rad_add = meta$RADA,
                                       szen = meta$SZEN)
```

### Save the corrected Landsat 8 data
Make sure that your saved dataset does only contain solar bands. Assuming that 
your normalized data is stored in variable `landsat_8_ac_rad`:
```{r}
landsat_8_ac_rad <- landsat_8_ac_rad[[...]]
writeRaster(landsat_8_ac_rad, 
            filename = paste0(inpath_l8, "l8_2013-07-07_30m_crop_ac_rad.tif"),
                              format = "GTiff")
```
