---
title: "W02-1: From DNs to physical units"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(raster)
library(rgdal)
library(sp)

library(devtools)
install_git("git://github.com/environmentalinformatics-marburg/satellite")
library(satellite)

inpath_l8 <- "D:/active/moc/am-remote-sensing/examples/data/landsat/l8_2013-07-07/"
```

### Reading croped Landsat 8 data
Read multi-layer geotiff in a stack and adjust the layer names to match the 
actual band numbers (assuming that you have followed W01-1 to the minute).
```{r}
landsat_8 <- stack(paste0(inpath_l8,"l8_2013-07-07_30m_crop.tif"))
bands <- names(landsat_8)
pos <- gregexpr(pattern ='crop', bands)[[1]][1]
bands <- paste0(substr(bands, 1, pos + 3), "_", c(1:7, 9:11))
names(landsat_8) <- bands
names(landsat_8)
```

### Get metadata information
Get calibration coefficients from the metadata file using function 
`satellite::compMetaLandsat`:
```{r}
# Your code here
```


### Converting band 3 and 10 to radiance
As an example, band 3 and 10 will be converted to radiance:
```{r}
# Your code here
```

### Converting band 3 to reflectance
As an example, band 3 will be converted to reflectance:
```{r}
# Your code here
```

### Converting band 10 to brightness temperature
As an example, band 10 will be converted to brightness temperature:
```{r}
# Your code here
```

